---
title: 'Dplyr verbs for lists and other verbs for data frames'
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dplyr verbs for lists and other verbs for data frames}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(dplyr)
library(lplyr)
```

## Verbs for lists and pairlists 

The package 'lplyr' extends some dplyr verbs to lists and pairlists: 

```{r}
xs <- list(x1 = 1:3, 
           x2 = 2:5, 
           x3 = "alpha")
```

```{r, eval = FALSE}
mutate(xs, x4 = 4) %>% str
rename(xs, x0 = x1) %>% str
```

Usual verbs made for standard evaluation work as well: 

```{r}
mutate_(xs, x4 = ~ 4) %>% str
rename_(xs, x0 = ~ x1) %>% str
```


## New verbs for data frames

The `mutate_which` and `transmute_which` functions are made for adding new variables or modifying existing ones on a subset of the data. 

```{r}
df <- mtcars[1:6,]
mutate_which(df, gear==4, carb = 100)
transmute_which(df, gear==4, carb = 100)
```

There is also a standard evaluation version of these functions, 
called `mutate_which_` and `transmute_which_`: 

```{r}
mutate_which_(df, ~ gear==4, carb = ~ 100)
transmute_which_(df, ~ gear==4, carb = ~ 100)
```

The function `pull` selects a column in a data frame 
and transforms it into a vector. 
This is useful to use it in combination with 
magrittr's pipe operator and dplyr's verbs.

```{r}
df[["mpg"]]
df %>% pull(mpg)

# more convenient than (mtcars %>% filter(mpg > 20))[[3L]]
df %>%
  filter(mpg > 20) %>%
  pull(3)
```
